---
name: Shubham
surname: Dutta, Ph.D.
position: "Scientist II"
address: "Massbiologics, University of Massachusetts Medical School"
phone: +1 (508) 502-0586
www: shubhamdutta.com
email: "shubhamdutta26@gmail.com"
orcid: 0000-0001-8484-0717
#researchgate: xxxxxxxxxxxxxxx
github: shubhamdutta26
linkedin: shubhamdutta26
date: "`r format(Sys.time(), '%B %Y')`"
#csl: apa-cv.csl # change this if you want to use other citation styles
output: 
  vitae::awesomecv #:
    #pandoc_args: ["--lua-filter=lua/strong.lua"] 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae);library(tibble)
#rmarkdown::pandoc_version()
```

# About me

 * Molecular Biologist with 10 years of experience in assay development
 * Designing & executing high-throughput CRISPR-Cas9 knockout & RNAi screens in cancer and rare genetic diseases
 * Experience in multicolor flow cytometry and flow panel design in blood
 * Design, production, and purification of monoclonal antibodies
 * Development and selection of stable clonal cell lines for protein production
 * Designing & executing antibody-antigen interaction studies using Surface Plasmon Resonance and BiLayer Interferometry
 * Supervising direct reports & working with cross-functional/ remote teams
 * Actively serving as a Editorial Board Member & Reviewer of several peer-reviewed journals

# Professional Experience

## Scientist II, Massbiologics, University of Massachusetts Medical School
2020 - Present

* Engineering novel antibodies against cell-surface markers in Neotropic non-human primates
* Generation and screening of hybridomas
* Production, purification, and quality testing of antibodies and proteins
* Generation of stable antibody producing cell lines
* High-throughput screening and identification of top expression clones
* Multicolor flow cytometry and panel generation for primate blood
* Managing research associates

## Scientist II, Totient Inc.
2018 - 2020

* Served as cell and molecular biology lead for oncology drug discovery programs
* Developed strategies to simultaneously knockout two genes using CRISPR-Cas9
* Experience with preparation of high-quality whole genome lentiviral sgRNA particles
* Identification of targets using CRISPR mediated whole genome knockout screen on multiple cell lines
* Identification of targets for recombinant antibodies using Protein arrays, western blotting, LC-MS, ELISA and immunofluorescence
* Worked with CROs with for special assays including 3D cell culture, Mass Spectrometry, and Surface Plasmon Resonance (SPR)
* Managed one direct report and one matrix reports in CROs

## Post-doctoral Associate, University of Massachusetts Medical School
2018

* Developing a CRISPR screen to identify novel epigenetic regulators of EWS-FLI1 fusion oncoprotein which causes Ewing’s sarcoma
* Executing genome wide shRNA/ RNAi and proteomic screens to identify transcription factors involved in X-chromosome inactivation
* Genome editing by CRISPR/Cas9 for specific projects in the lab
* Managed one intern and two junior graduate students

\pagebreak

# Education

```{r}
tribble(
  ~ Degree,
  ~ Advisor,
  ~ Year,
  ~ Institution,
  ~ Where,
  "Doctor of Philosophy, Biomedical Sciences",
  NA,
  "09/2011-06/2018",
  "University of Massachusetts Medical School",
  "Worcester, MA, USA",
  "Master of Science, Biophysics and Molecular Biology",
  NA,
  "06/2008-05/2010",
  "University of Calcutta",
  "Calcutta, West Bengal, India",
  "Bachelor of Science, Microbiology",
  NA,
  "06/2005-05/2008",
  "University of Calcutta",
  "Calcutta, West Bengal, India",
) %>%
  detailed_entries(
    what = Degree,
    when = Year,
    with = Institution,
    where = Where,
    why = Advisor
  )
```

# Publications

```{r}
bibliography_entries("citations.bib")
```

